Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-02 latex/appendix.tex
lyx

@@

>>>>

	\item [!] revise HM. align dap dan directly instead of the loss.

	\item [!] re-design Gradual Adversary for HM based on that for the amdsemi.

	\item [!] difference between EST, ACT, AMD/ AMDsemi.
		Other methods (than HM) cannot effectively learn from the strongest
		adversary as the inner maximization is indirectly (and not guaranteed).
		HM follows the min-max paradigm (can be incorporated into FAT etc).
		Both ACT and HM stops at a specific point.

@@

	\item [?] adversarial training that does not allow embedding move may
		encourage model collapse. Maybe we just apply some loosened restrction
		such as aap? i.e. $(a,\tilde{a},p;\gamma=0)$.
